Untwisting the Boerdijk--Coxeter

### 2017-04-12 doc/TetrahelixUntwist.tex
adding new figure and TODOs at end

This formula defines a helix, but it is not any of the apparent helices, or \emph{rail} helices, of the
BC helix, but rather one that winds three times as rapidly through all
nodes. To a designer of tetrahelices, it is more natural to think of
the three helices which are visually apparent, that is, those three
which are closely approximated by the outer edges or rails of
the BC helix. We think of each of these three rails as being a different color: red, blue, or yellow.

@@

Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued.)

@@

Writing as robotocists, the ``colored'' approach of thinking of three rails seems natural to us, in part because our application
is focused on the edges, rather than any sort of interpretaion of the tetrahedra as solids. \Cref{eq:general} is in terms of helices that are close
to what you see when you look at a tetrahelix constructed from edges.
Having proved \cref{generalformulaoptimal}, it becomes plain that one could also use
 a generalization of the orginal Coxeter/Gray formulation which uses a single helix to define all vertices, and a mathematician, chemist,
or solid modeler might prefer that. This formulation is equivalent to \Cref{eq:general}, but uses $\theta = \frac{\rho+ 2\pi}{3}$,
the rotation between rails, and triples the rotation rate. The same constraint on $r_{opt}$ and $d_{opt}$ holds if the user seeks minimax optimality.

@@

If an equitetrabeam were actually
used as a beam, an engineer might start with the optimal tetrabeam and
dilate it in one dimension to ``deepen'' the beam. Similarly, simple
length changes curve the equitetrabeam into an ``arch''.

@@

Improve Figures

>>>>

This formula defines a helix, but it is not any of the apparent helices, or \emph{rail} helices, of the
BC helix, but rather one that winds three times as rapidly through all
nodes. To a designer of tetrahelices, it is more natural to think of
the three helices which are visually apparent, that is, those three
which are closely approximated by the outer edges or rails of
the BC helix. We think of each of these three rails as being a different color: red, blue, or yellow.
This situation is illustrated in \cref{fig:helixcomparison}, wherein the black helix represents that
generated by \cref{graycoxeter},
and the colored helices are generated by \cref{eq:colored}.

\begin{figure}
  \centering
     \includegraphics[width=0.7\textwidth]{figures/HelixComparison.png}
     \caption{Rail helices vs. Coxeter/Gray helix}
  \label{fig:helixcomparison}  
\end{figure}

@@

Recall that $c \in \{0,1,2\}$, but $n$ is continuous (rational or real-valued.)
We can now assert that in \cref{fig:helixcomparison} the black helix winds at
$\frac{3 \theta_{bc}}{\rho_{bc}} \approx 11.16 $ times the rate of a rail helix.

@@

Writing as robotocists, the ``colored'' approach of thinking of three rails seems natural to us,
in part because our application
is focused on the edges, rather than any sort of interpretaion of the tetrahedra as solids.
\Cref{eq:general} is in terms of helices that are close
to what you see when you look at a tetrahelix constructed from edges.
Having proved \cref{generalformulaoptimal}, it becomes plain that one could also use
a generalization of the orginal Coxeter/Gray formulation which uses a single helix
to define all vertices, and a mathematician, chemist,
or solid modeler might prefer that. This formulation is equivalent to \Cref{eq:general},
but uses $\theta = \frac{\rho+ 2\pi}{3}$,
the rotation between rails. The same constraint on $r_{opt}$ and $d_{opt}$ holds if the user seeks minimax optimality.

@@

If an equitetrabeam were actually
used as a beam, an engineer might start with the optimal tetrabeam and
dilate it in one dimension to ``deepen'' the beam. Similarly, simple
length changes curve the equitetrabeam into an ``arch''.
The ``colored'' approach of \cref{eq:general} exposes these possibilities
more than the approach of \cref{eq:coxtergraygeneral}.

@@

Improve the helix comparison by constructing by hand in the Inkscape.

Check the math on V_{general}.

Reread everything, especially the new parts.

Introduct the torsion concept.
